\TitlePt

### 2016-03-28 paper-tesseroids.tex
Place urls from footnotes in the text
This is how the rest of the thesis is, so might as well be consistent

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online\footnote{
\url{http://tesseroids.leouieda.com}}\footnote{
\url{http://dx.doi.org/10.5281/zenodo.16033}}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in an online repository\footnote{
\url{https://github.com/pinga-lab/paper-tesseroids}}.

>>>>

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online
(\url{http://tesseroids.leouieda.com} or
\url{http://dx.doi.org/10.5281/zenodo.16033})
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in the online repository
\url{https://github.com/pinga-lab/paper-tesseroids}.
